From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-13 Pi+/paper/finite.tex
More on the coxeter relation

\begin{definition}
  Let $A$ be a type, and $\List(A)$ the free monoid on $A$. The free group $F(A)$ on $A$ is the set-quotient of
  $\List(A + A)$ by the congruence closure of the relation $(\inl(a) \cons \inr(a) \cons \nil) \sim \nil$.
\end{definition}

@@

We define a binary relation on $\List(\Fin[n])$.

@@

We define $\cox*$ as the congruence closure of $\cox$.

\vc{This could be simplified a bit depending on our formalisation.}

@@

The type $\Sn$ is defined as the set-quotient of $\List(\Fin[n])$ by $\cox*$.
q
\begin{definition}[$\Sn$]
  \(\Sn \defeq \quot{\List(\Fin[n])}{\cox*}\)
\end{definition}

@@

\begin{proposition}
  $\Sn$ is equivalent to the generated group given by the normal closure of $\cx$ extended to $\List(\Fin[n] + \Fin[n])$
  along the codiagonal map $[\term{id},\term{id}] : A + A \to A$.
\end{proposition}

>>>>

\begin{definition}
  Let $A$ be a type, and $\List[A]$ the free monoid on $A$. The free group $F(A)$ on $A$ is the set-quotient of
  $\List[A + A]$ by the congruence closure of the relation $(\inl(a) \cons \inr(a) \cons \nil) \sim \nil$.
\end{definition}

@@

We define a binary relation on $\List[\Fin[n]]$.

@@

We define $\cox*$ as the congruence closure of $\cox$.
\vc{This could be simplified a bit depending on our formalisation. $\cox$ is directed, use a different symbol?}

@@

We state and prove two desirable properties of this relation on $\List[\Fin[n]]$ from the point of view of an abstract
rewriting system. We follow the terminology of~\cite{krausCoherenceWellFoundednessTaming2020}.
\vc{Not completely formalised.}

\begin{proposition}
  \leavevmode
  \begin{enumerate}
    \item $\cox$ is (locally) confluent. For every span $w_{1} \cox w \cox w_{2}$, there is a matching extended cospan
          $w_{1} \cox* v \cox* w_{2}$.
    \item $\cox*$ is strongly normalising. For every $w$, there exists a unique $v$ such that $w \cox* v$. Equivalently,
          the type $\dsum{v:\List[\Fin[n]]}{w \cox* v}$ is contractible, and $w \cox* v$ is a proposition for every $w$
          and $v$.
  \end{enumerate}
\end{proposition}

The type $\Sn$ is defined as the set-quotient of $\List[\Fin[n]]$ by $\cox*$.

\begin{definition}[$\Sn$]
  \(\Sn \defeq \quot{\List(\Fin[n])}{\cox*}\)
\end{definition}

@@

\begin{proposition}
  $\Sn$ is equivalent to the generated group given by the normal closure of $\cox*$ extended to $\List(\Fin[n] + \Fin[n])$
  along the codiagonal map $[\term{id},\term{id}] : A + A \to A$.
\end{proposition}
